\sysfull

### 2017-08-03 paper/background.tex
Kiwan's compiler section revised - really nice text Kiwan

%\TODO{This sequential/modular split seems pretty odd to me. I think we can just talk about tasks in the sense of ratchet, alpaca, and chain.  Anything with static (programmer-written or compiler inserted) boundaries applies}
Task-based intermittent execution models~\cite{dino,chain,alpaca} ask the
programmer to decompose their program into a collection tasks. A task is a
function with no caller that contains arbitrary computation, sensing, and
communication.  A programmer describes the sequence in which tasks may execute,
creating a task graph. The flow of control from task to task happens at
programmer demarcated points and may conditionally depend on program values.
Task-based programming abstractions guarantee that tasks exhibit behavior as
though they executed {\em atomically}, regardless of arbitrary power failures.
Task-based runtime systems tolerate failures by repeatedly attempting to
execute a task until it completes. Task-based runtime systems ensure
task-atomic semantics by ensuring that repeated task executions are idempotent
(i.e., have the same effect when repeatedly executed).  The key to idempotence
is ensuring that updates to non-volatile state made by an interrupted, partial
execution of a task are never visible to a subsequent (potentially completing)
re-execution of the task.

There are several run time strategies to ensuring task idempotence. One
approach~\cite{alpaca} is to identify non-volatile data involved in WAR
dependences in a task (like DINO and Ratchet did for
checkpoints~\cite{dino,ratchet}), execute the task using buffered copies of
those data, and commit the buffered copies before completing the task. Another
strategy is to statically create multiple versions of non-volatile data shared
by tasks and ensure by construction that no task reads and writes the same
non-volatile memory location~\cite{chain}.  Regardless of the idempotence
strategy, the key to task-based execution is that fixed, statically defined
tasks execute as though atomic, completing after zero or more attempts.

\TODO{Brandon left off here.}

>>>>

%\TODO{This sequential/modular split seems pretty odd to me. I think we can just talk about tasks in the sense of ratchet, alpaca, and chain. Anything with static (programmer-written or compiler inserted) boundaries applies}

Task-based intermittent execution models~\cite{dino,chain,alpaca} ask the programmer to decompose their program into a collection tasks. A task is a function with no caller that contains arbitrary computation, sensing, and communication. A programmer describes the sequence in which tasks may execute,
creating a task graph. The flow of control from task to task happens at programmer demarcated points and may conditionally depend on program values. Task-based programming abstractions guarantee that tasks exhibit behavior as though they executed {\em atomically}, regardless of arbitrary power failures. Task-based runtime systems tolerate failures by repeatedly attempting to execute a task until it completes. Task-based runtime systems ensure task-atomic semantics by ensuring that repeated task executions are idempotent (i.e., have the same effect when repeatedly executed). The key to idempotence is ensuring that updates to non-volatile state made by an interrupted, partial execution of a task are never visible to a subsequent (potentially completing) re-execution of the task.

There are several run time strategies to ensuring task idempotence. One approach, utilized by Alpaca~\cite{alpaca}, is to identify non-volatile data involved in WAR dependences in a task (like DINO~\cite{dino} and Ratchet~\cite{rachet} did for checkpoints), execute the task using buffered copies of those data, and commit the buffered copies before completing the task. Another strategy is to statically create multiple versions of non-volatile data shared by tasks and ensure by construction that no task reads and writes the same non-volatile memory location~\cite{chain}. Regardless of the idempotence strategy, the key to task-based execution is that fixed, statically defined tasks execute as though atomic, completing after zero or more attempts. \TODO{Brandon left off here.}

### 2017-08-03 paper/evaluation.tex
Kiwan's compiler section revised - really nice text Kiwan

Expected results:
\begin{itemize}
	\item comparison between manual (Chain code) and automatic taskification: in terms of code SLOCs, number of tasks, completion time (Chain), memory use (other metrics required?)
	\item assessment of correctness (through manual inspection only?).
\end{itemize}

@@

>>>>

Expected results:
\begin{itemize}
	\item comparison between manual (Chain code) and automatic taskification: in terms of code SLOCs, number of tasks, completion time (Chain), memory use (other metrics required?), show number of LLVM instructions per energy cycle
	\item assessment of correctness (through manual inspection only?).
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\caption{Initial figure about page size overhead. \todo{Figure placeholder---will be replaced with final one}{Amjad}}
	\label{fig:IPOSPerformance}
\end{figure}
